BayesPy: Variational Bayesian Inference in Python

### 2015-06-05 bayespy.tex
Fix minor typos

The speed of the packages were compared by using two widely used models: a
Gaussian mixture model (GMM) and principal component analysis
(PCA).\footnote{The scripts for running the experiments are available as
  supplementary material.}  Both models were run for small and large artificial
datasets.  For GMM, the small model used 10 clusters for 200 observations with 2
dimensions, and the large model used 40 clusters for 2000 observations with 10
dimensions.  For PCA, the small model used 10-dimensional latent space for 500
observations with 20 dimensions, and the large model used 40-dimensional latent
space for 2000 observations with 100 dimensions.  For the PCA model, Infer.NET
used both a fully factorizing approximation and also the same approximation as
in BayesPy which did not factorize with respect to the latent space dimensions.
%Infer.NET used a fully factorizing approximation for the PCA model,
%whereas BayesPy did not factorize with respect to the latent space dimensions.  
The experiments were run on a quad-core (i7-4702MQ) Linux computer.
% with a quad-core processor (i7-4702MQ).
Because the packages run practically identical algorithms and thus
converged to similar solutions in a similar number of iterations (50--100
iterations depending on the dataset), we compared the average CPU time per
iteration.

@@

\begin{table}[tb]
  \centering
  \caption{
    The average CPU time in milliseconds per iteration for each
    dataset.  The results in parentheses have the following meanings: a) BayesPy without using
    broadcasting. b) Infer.NET using the same factorization as in
    BayesPy.
  }
  \small
  \begin{tabular}{ccccc}
    &
    Small GMM
    &
    Large GMM
    &
    Small PCA
    &
    Large PCA
    \\
    \hline
    BayesPy     & 6 & 90  & 7 (60) & 400 (1\,500)
    \\
    Infer.NET   & 25 & 4\,600 & 37 (350) & 2\,200 (210\,000)
  \end{tabular}
  \label{tab:speed}
\end{table}

>>>>

The speed of the packages were compared by using two widely used models: a
Gaussian mixture model (GMM) and principal component analysis
(PCA).\footnote{The scripts for running the experiments are available as
  supplementary material.}  Both models were run for small and large artificial
datasets.  For GMM, the small model used 10 clusters for 200 observations with 2
dimensions, and the large model used 40 clusters for 2000 observations with 10
dimensions.  For PCA, the small model used 10-dimensional latent space for 500
observations with 20 dimensions, and the large model used 40-dimensional latent
space for 2000 observations with 100 dimensions.  For the PCA model, Infer.NET
used both a fully factorizing approximation and also the same approximation as
BayesPy which did not factorize with respect to the latent space dimensions.
%Infer.NET used a fully factorizing approximation for the PCA model,
%whereas BayesPy did not factorize with respect to the latent space dimensions.  
The experiments were run on a quad-core (i7-4702MQ) Linux computer.
% with a quad-core processor (i7-4702MQ).
Because the packages run practically identical algorithms and thus
converged to similar solutions in a similar number of iterations (50--100
iterations depending on the dataset), we compared the average CPU time per
iteration.

@@

\begin{table}[tb]
  \centering
  \caption{
    The average CPU time in milliseconds per iteration for each
    dataset.  The results in parentheses have the following meanings: a) BayesPy without using
    broadcasting. b) Infer.NET using the same factorization as
    BayesPy.
  }
  \small
  \begin{tabular}{ccccc}
    &
    Small GMM
    &
    Large GMM
    &
    Small PCA
    &
    Large PCA
    \\
    \hline
    BayesPy     & 6 & 90  & 7 (60) & 400 (1\,500)
    \\
    Infer.NET   & 25 & 4\,600 & 37 (350) & 2\,200 (210\,000)
  \end{tabular}
  \label{tab:speed}
\end{table}
